---
title: "{{ DOCUMENT_TITLE }}"
date: "{{ TODAY_DATE }}"
output: html_document
---

## Dataset: {{ DATASET_TITLE }}

{{ DATASET_DESCRIPTION }}

{{ SSZ_COMMENTS }}

{{ DATASHOP_LINK_PROVIDER }}<br>
{{ DATASHOP_LINK_ORGANIZATION }}

Auto generated R starter code for data set {{ DATASET_IDENTIFIER }}.

## Metadata

{{ DATASET_METADATA }}

# Load packages

```{r}

library(tidyverse)
library(skimr)
library(sf)

```

# Load data

-   The dataset has {{ DISTRIBUTION_COUNT }} distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Helper function to get available layers from WFS
get_wfs_layers <- function(url) {
  dataset_identifier <- sub(".*/(.*)\\?.*", "\\1", url)
  url_geoportal <- paste0("https://www.ogd.stadt-zuerich.ch/wfs/geoportal/", dataset_identifier)
  
  cat("Getting available layers from:", url_geoportal, "\n")
  
  params <- list(service = "WFS", version = "1.1.0", request = "GetCapabilities")
  
  response <- httr::GET(url_geoportal, query = params)
  content <- httr::content(response, as = "text", encoding = "UTF-8")
  
  layers <- xml2::read_xml(content) %>%
    xml2::xml_find_all(".//wfs:FeatureType/wfs:Name", xml2::xml_ns(content)) %>%
    xml2::xml_text()
  
  cat("Available layers:", paste(layers, collapse = ", "), "\n")
  
  return(layers)
}

# Fetch available layers
layers <- get_wfs_layers("{{ DISTRIBUTIONS }}")

# Set first layer as default
typename <- layers[1]
cat("Chosen typename:", typename, "\n")

# Construct WFS request URL
wfs_url <- paste0("{{ DISTRIBUTIONS }}&service=WFS&version=1.1.0&request=GetFeature&typename=", typename, "&outputFormat=application/json")

# Load GeoJSON data
df <- st_read(wfs_url)

```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

# Drop empty columns
df <- df %>% select(where(~!all(is.na(.))))

# Print dataset info
cat(sprintf("The dataset has %d rows (observations) and %d columns (variables).\n", nrow(df), ncol(df)))
cat(sprintf("There seem to be %d exact duplicates in the data.\n", sum(duplicated(df))))

# Memory usage
tibble::glimpse(df)
```

# Plot data

```{r}
plot(df$geometry)
```
# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

{{ CONTACT }}
