---
title: "{{ DOCUMENT_TITLE }}"
date: "{{ TODAY_DATE }}"
output: html_document
---

## Dataset: {{ DATASET_TITLE }}

{{ DATASET_DESCRIPTION }}

{{ SSZ_COMMENTS }}

{{ DATASHOP_LINK_PROVIDER }}

Auto generated R starter code for data set {{ DATASET_IDENTIFIER }}.

## Metadata

{{ DATASET_METADATA }}

# Load packages

```{r}
library(httr2)
library(sf)
library(skimr)
library(tidyverse)
library(xml2)
```

# Load the data

data link
```{r}
url <- "{{ FILE_URL }}"
```


Helper function to create the url based on the geoportal, as the files are not directly available via fixed link like csvs.
```{r}
get_geoportal_url <- function(url) {
  dataset_identifier <- sub(".*/(.*)\\?.*", "\\1", url)
  paste0("https://www.ogd.stadt-zuerich.ch/wfs/geoportal/", dataset_identifier)
}
```

```{r}
# Helper function to get available layers from WFS
get_wfs_layers <- function(url) {
  
  url_geoportal <- get_geoportal_url(url)
  
  cat("Getting available layers from:", url_geoportal, "\n")
  
  # read xml from geoportal
  resp <- request(url_geoportal) |> 
    req_headers(service = "WFS", version = "1.1.0", request = "GetCapabilities") |> 
    req_perform()
  
  content_as_xml <- resp_body_xml(resp)
  
  # find available layers: find "Name" nodes with parent "Layer"
  name_nodes <- content_as_xml |> xml_ns_strip() |> xml_find_all("//Name")
  
  # keep all nodes that have Name and it's parent's name is "Layer"
  # and directly extract the name to get a list of typenames
  typename_nodes <- purrr::keep(name_nodes,
                                \(x) xml_name(xml_parent(x)) == "Layer")
  
  return(typename_nodes)
}

# Fetch available layers
layers <- get_wfs_layers(url)

# Set first layer as default
typename <- xml_text(layers[[1]])
cat("Chosen typename:", typename, "\n")
```

read the data
```{r}
read_geodata <- function(url, typename) {
  url_geoportal <- get_geoportal_url(url)
  
  request <- request(url_geoportal) |>
    req_url_query(
      service = "WFS",
      version = "1.1.0",
      outputFormat = "GeoJSON",
      request = "GetFeature",
      typename = typename
    )
  
  st_read(request$url)
}

df <- read_geodata(url, typename)
```

if the approach above does not work, try using [ows4r](https://eblondel.github.io/ows4R/); however, this needs to be installed first
```{r eval=FALSE}
# install.packages("ows4R")
library(ows4R)

# WFS-Client erstellen
url_geoportal <- get_geoportal_url(url)
wfs_client <- WFSClient$new(url_geoportal, "1.1.0")

# Verfügbare Feature-Typen anzeigen
wfs_client$getFeatureTypes(pretty = TRUE)

typenames <- wfs_client$getFeatureTypes(pretty = TRUE) |> 
  dplyr::pull(name)

df <- read_geodata(url, typenames[[1]])
```

# Analyze the data

look at the data
```{r}
head(df)
```

```{r}
glimpse(df)
```

```{r}
# look at distributions etc. without looking at geographical data (skim cannot deal with geometries)
skim(st_drop_geometry(df))
```

# Plot data

base R plot
```{r}
plot(df$geometry)
```

ggplot2 plot
```{r}
df |>
  ggplot() +
  geom_sf()
```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Contact

{{ CONTACT }}
